Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2017-09-20 paper/paper.Rmd
Latex cross tables

---
title: "Detecting Facial Expressions in Video Stills from Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
date: "28 July 2017"
output: bookdown::pdf_document2
toc: false
fig_caption: yes
number_sections: false
fontsize: 11pt
documentclass: article
bibliography: references.bib
biblio-style: apalike
link-citations: true
---

@@

\begin{table}[htp]
%\parbox{.5\linewidth}{
\caption{Counts of captures of different APIs against manually tagged faces.}
\label{tab:facecounts}
\centering
\begin{tabular}{ccccccc}
\cline{1-3}\cline{5-7} 
\multicolumn{3}{c}{Animetrics}&&\multicolumn{3}{c}{Google}\\\cline{1-3}\cline{5-7}
Manual & Face & No Face & & Manual & Face & No Face\\ 
%heading
\cline{1-3}\cline{5-7} 
Face & 434 & 1861 & & Face & 1319 & 976\\
NoFace &527 & 787 & & NoFace &638 & 676 \\\cline{1-3}\cline{5-7}
\end{tabular}
\\[1.5ex]
\begin{tabular}{ccccccc}
\cline{1-3}\cline{5-7} 
\multicolumn{3}{c}{Animetrics}&&\multicolumn{3}{c}{Google}\\\cline{1-3}\cline{5-7}
Manual & Face & No Face & & Manual & Face & No Face\\ 
%heading
\cline{1-3}\cline{5-7} 
Face & 434 & 1861 & & Face & 1319 & 976\\
NoFace &527 & 787 & & NoFace &638 & 676 \\\cline{1-3}\cline{5-7}
\end{tabular}
\end{table}

>>>>

---
title: "Detecting Facial Expressions in Video Stills from Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
date: "20 September 2017"
output: bookdown::pdf_document2
toc: false
fig_caption: yes
number_sections: false
fontsize: 11pt
documentclass: article
bibliography: references.bib
biblio-style: apalike
link-citations: true
---

@@

\begin{table}[htp]
%\parbox{.5\linewidth}{
\caption{Counts of captures of different APIs against manually tagged faces.}
\label{tab:facecounts}
\centering
\begin{tabular}{ccccccc}
\cline{1-3}\cline{5-7} 
\multicolumn{3}{c}{Animetrics}&&\multicolumn{3}{c}{Google}\\\cline{1-3}\cline{5-7}
Manual & Face & No Face & & Manual & Face & No Face\\ 
%heading
\cline{1-3}\cline{5-7} 
Face & 434 & 1861 & & Face & 1319 & 976\\
NoFace &527 & 787 & & NoFace &638 & 676 \\\cline{1-3}\cline{5-7}
\end{tabular}
\\[1.5ex]
\begin{tabular}{ccccccc}
\cline{1-3}\cline{5-7} 
\multicolumn{3}{c}{Microsoft}&&\multicolumn{3}{c}{Skybiometry}\\\cline{1-3}\cline{5-7}
Manual & Face & No Face & & Manual & Face & No Face\\ 
%heading
\cline{1-3}\cline{5-7} 
Face & 565 & 1730 & & Face & 493 & 1802\\
No Face &505 & 809 & & No Face &512 & 802 \\\cline{1-3}\cline{5-7}
\end{tabular}
\end{table}
